\documentclass[12pt]{article}
\usepackage{fontspec}
\setmainfont{DejaVu Sans}
\usepackage[cm]{fullpage}
\usepackage{graphicx}
\usepackage{tikz}

\begin{document}
\title{CS22310 Hotel Project}
\author{Felix Farquharson}

\maketitle
\tableofcontents

\section{Introduction}
The purpose of this project is to create a prototype hotel booking system
that follows all usability pricipals. Careful attention was to be paid to
the general layouts and navigation parts of the website.

We were to carry a full task analysis, create a full prototype and discuss
general issues and improvements on what we had created at the end of the 
project.

\section{Task Analysis}
\subsection{Needs of System}
There are many reasons to implement a system such as this. Two of the most
significant reasons are: That it will reduce the workload on staff that 
deal with bookings which may lead to lower costs. Also it will improve 
your customer reach by being available 24/7.

An analysis of further needs follows.

\subsection{Who is involved (Target Audience)?}
Obviously there are a number of different parties that will be affected by
the implimentation of a computer based system. The two most obvious will be
hotel staff and potential customers to the business.
\subsubsection{Rich Picture}
A rich picture has been produced to illistrate the different people who will
be affected by the new system.

\input{diagrams/rich_pic.tex}

\subsubsection{Hotel Staff}
There many types of hotel staff that may need to use the system.
\paragraph{Bookings Staff}
The bookings staff will be the primary staff users of the system because
they will be the ones who have to input all of the information for the 
people who choose not to book online. For example every one that phones up
to make, adjust or cancel a booking will have to speak to these staff.

The bookings staff or receptionists will have to input into their system
when someone arrives to stay in one of the rooms.

The Bookings staff can afford to spend a little longer learning how to use
the system if it makes it more efficient for them to use in the long run.
The primary factor is going to be speed of use.

\paragraph{Management}
Management staff need to be able to use the system to make sure that targets
are being met and that their staff are doing their jobs properly. They may 
also need to use the system to deal with customer complaints and checking that
the rooms are being used correctly.

\paragraph{Cleaning Staff}
Cleaning staff will have to clean all of the rooms that have been slept in.
It would make sense for them to be able to use the system to fin out which
rooms have been used and therefor which ones need to be cleaned.

\subsubsection{General Public}
The general public may use the system to find out about up to date pricing
and available rooms for rental. The look/feel and usability of the system 
will effect their opinion of the hotel.

\subsubsection{Potential Customers}
Potential customers will need to be able to find out about costs and to place
a booking that suits their needs. The may also need to adjust the booking in 
the future and cancel the booking if they no longer need it.

\subsubsection{Auditors and Investigators}
If the hotel is run as a business then there will be taxes to pay. These taxes
may depend on how much business there has been throughout the year. These 
statistics may be produced by the bookings system. It would be convenient
if the system could produce accounts of what has happened through the year.
It may also be useful for business planning because it could show the amount
of occupied rooms around the year, the busiest times of year and the discounts
that have been made etc.

\subsection{Booking Systems in Existance}
\begin{description}
	\item[Eviivo Frontdesk] Popular hotel and B\&B booking system. 
		It provides a high level of security, customer reviewing,
		web space to present the business and financial graphs. 
		http://www.eviivo.com/our-products/eviivo-frontdesk/
	\item[Guestmaster] Different versions for different hotels.
		It provides mail merge and special offer support. It also
		automatically backs up records. Which is quite important.
		http://www.guestmaster.com/
\end{description}

\subsection{Usability Expectations}
\subsubsection{Description of Available Functions}
\begin{description}
	\item[Web space] Allows you to present your business to the
		customers so that they can get an impression of your hotel
		before they start the booking process. It is important that
		the impression is good, otherwise this may act as a negtive
		point.
	\item[Online information gathering] This is particularly important
		because without it you would have very little to make up a
		booking system. This information is then stored and must be
		available in the correct places to make sure that the
		program is usable. The information must allow the system
		to \"learn\".
	\item[Online payment] The users should be able to pay for their
		accomadation online otherwise it would be more complicated
		to complete the booking process.
	\item[]
\end{description}

\subsubsection{Additional Functions}
\subsection{Use Case Diagram}
\subsection{Data Flow Diagram}
\subsection{State Transition Diagram}
\subsection{Project Feesability}
\subsubsection{Costs and Resources Required}
\subsubsection{Known Constraints and Assumptions}

\section{Design}
\subsection{Layouts}
\subsection{Navigation}
\subsection{Other Pricipals Used}

\section{Prototype}

\section{Discussion}

\end{document}